\newpage
\section*{Checklists}
\paragraph{}Taken from Polo's \href{https://docs.google.com/document/u/0/d/e/2PACX-1vSlYrMw402tL3F95ay-AaptTdF80UOER-gne_O0kqbuuk6WXrlsjwaYjjS0Jyl95dXYyDLjh9DR1mln/pub?pli=1}{doc}. This section will be hidden if the global variable \texttt{showtodo} (located in \texttt{./config.sty}) is set to \texttt{disable}.

\subsection*{Doc Specs}

\alertblock{checklist}{Doc Appearance}{Margin $\geq1$ inch, fontsize $\geq11$ pts, $\leq2$ pages (w.o. bibliography).}
\alertblock{status}{Doc Appearance}{Margin, fontsizes are configured (using the \texttt{geometry} package). Number of pages will be known only after contents are filled in.}
\alertblock{checklist}{Doc Metadata}{Include team number, member names, project title.}
\alertblock{status}{Doc Metadata}{Team numbers: \faCheck. Team member Names: would recommend using full names. Need to think of a project title.}
\alertblock{checklist}{Doc Filename}{The uploaded proposal file name needs to be \texttt{team0{\teamNum}proposal.pdf}.}

\subsection*{Project Content}
\alertblock{checklist}{Topic}{Interesting, relevant to course, of suitable difficulty. Justify it.}
\alertblock{checklist}{Dataset}{Large and Real, e.g. couple hundreds of thousand of rows, couple hunderd MBs.}
\alertblock{checklist}{Analysis}{Perform non-trivial algorithm/analysis/computation.}
\alertblock{checklist}{Interactivity}{Build an interactive user interface.}

\subsection*{Heilmeier}
\alertblock{checklist}{Heilmeier Q1}{What are you trying to do? Articulate objectives, no jargon.}
\alertblock{checklist}{Heilmeier Q2}{How is it done today; what are the limits of current practice?}
\alertblock{checklist}{Heilmeier Q3}{What’s new in your approach? Why will it be successful?}
\alertblock{checklist}{Heilmeier Q4}{Who cares?}
\alertblock{checklist}{Heilmeier Q5}{If you’re successful, what difference and impact will it make, and how do you measure them (e.g., via user studies, experiments, ground truth data, etc.)?}
\alertblock{checklist}{Heilmeier Q6}{What are the risks and payoffs?}
\alertblock{checklist}{Heilmeier Q7}{How much will it cost?}
\alertblock{checklist}{Heilmeier Q8}{How long will it take?}
\alertblock{checklist}{Heilmeier Q9}{What are the midterm and final "exams" to check for success? How will progress be measured?}

\subsection*{Section-wise checklists: Literature Survey}
\alertblock{checklist}{Literature Survey Content}{Each survey needs to describe the main idea, useful (or uselessness) to our project, potential shortcomings.}
\alertblock{checklist}{Literature Survey Source Length}{Should add up to 18 papers, with short papers (PNAS, Nature, Science) count as 0.5.}
\alertblock{checklist}{Literature Survey Integrity}{Do not copy abstracts.}
\alertblock{checklist}{Literature Survey Citations}{Cite References.}

\subsection*{Section-wise checklists: Expected Innovations}
\paragraph{}Add if needed.

\subsection*{Section-wise checklists: Plan of Activities}
\alertblock{checklist}{Plan Chart / Table}{A Gantt chart or table, describing past and future activities of members with start/end time.}
\alertblock{checklist}{Plan Statement}{Place after table / Gantt chart. Summarize distribution of team members’ effort. Things like "everyone contributed similar amount of effort" is fine.}
